Figures_MSA-PD

### 2024-12-04 Manuscript_figures.Rmd
Updated `Manuscript_figures`

---
title: "Figures_MSA-PD"
author: "Rasmus Rydbirk"
date: "03-12-2024"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

@@

# qsave(anno.major, "/work/msa/03_annotations/anno_0final.qs")

@@

```{r}
con.glia <- qread("/work/msa/02_data/conos/con_oligo_astro_opc.qs", nthreads = 10)

@@

We provide the results from scDRS based on Nalls *et al.* GWAS summary stats.

@@

We provide the results from scDRS based on Chia *et al.* GWAS summary stats.

>>>>

---
title: "Figures_MSA-PD"
author: "Rasmus Rydbirk"
date: "04-12-2024"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

@@

@@

```{r}
con.glia <- qread("con_oligo_astro_opc.qs", nthreads = 10)

@@

We provide the results from scDRS based on Nalls *et al.* GWAS summary stats. For calculation of these, see `scDRS_PD.ipynb`.

@@

We provide the results from scDRS based on Chia *et al.* GWAS summary stats. For calculation of these, see `scDRS_MSA.ipynb`.
